The Design, Semantics, and Implementation of the Synchronous Language \CEU

### 2016-03-27 paper.tex
...

@@

@@

On the one hand, enforcing an execution order for concurrent operations may 
seen arbitrary and also precludes true parallelism.
On the other hand, it provides a priority scheme for trails, and makes 
shared-memory concurrency more tractable.
%
For constrained embedded development, we believe that deterministic 
shared-memory concurrency is beneficial, given the extensive use of memory 
mapped ports for \emph{I/O} and the lack of hardware support for real 
parallelism.

>>>>

TODO: recover the logical notion of simultaneaty substituting 200ms with TICK

@@

TODO: move POE to here, simpler more natural for software dev

- static analsysis also simpler
    - highlight that is not only important to have a comptutally-sound 
      algorithm, but that something that programmers can understand
- same with 1st-class timers, also, too much common to be ignored

@@

On the one hand, enforcing an execution order for concurrent operations may 
seen arbitrary and also precludes true parallelism.
On the other hand, it provides a priority scheme for trails, and makes 
shared-memory concurrency more tractable.
    - again, simple
%
For constrained embedded development, we believe that deterministic 
shared-memory concurrency is beneficial, given the extensive use of memory 
mapped ports for \emph{I/O} and the lack of hardware support for real 
parallelism.
